\Large \bf Module-level Dynamic Analysis

### 2019-12-19 paper/draft.tex
Update packages

\usepackage{tikz}
\usepackage{amsmath}

%-------------------------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------------------------

@@

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Module-aware Fracture and Recombination for Dynamic Analysis}

@@

\begin{abstract}
  One two three
\end{abstract}

>>>>

\usepackage{soul}
\usepackage{xspace}
\usepackage{color}
\newcommand{\eg}{{\em e.g.}, }
\newcommand{\ie}{{\em i.e.}, }
\newcommand{\etc}{{\em etc.}\xspace}
\newcommand{\vs}{{\em vs.} }

\newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
\newcommand{\sx}[1]{(\S\ref{#1})}
\newcommand{\sys}{{\scshape Lya}\xspace}
\newcommand{\toy}{{\tt lya.js}\xspace}
%-------------------------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------------------------

@@

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Module-level Dynamic Analysis}

@@

\begin{abstract}
We introduce \emph{module-level dynamic analysis}, a new dynamic analysis abstraction that supports dynamic fracture and recombination at the level of individual modules.
By leveraging the ubiquity of third-party modules in today's applications, this analysis provides 
Our implementation, \sys, simplifies the analysis

\end{abstract}
